Red-Giant Hot Jupiters: Brilliant Radio Beacons

### 2015-03-22 ms.tex
authors
fixed typo
Added Project Florida Labs to my affiliation.

\author{
%
David S. Spiegel\altaffilmark{1} \\
%
{\bf and some order:} \\
%
Nikku Madhusudhan\altaffilmark{?} [Add correct affiliation] \\
%
Mehrdad Mirbabayi\altaffilmark{1} \\
%
Aaron Parsons\altaffilmark{?} [Add correct affiliation] \\
%
Tony Mroczkowski\altaffilmark{?} [Add correct affiliation]
}

@@

\affil{$^?$Astronomy Department, University of Cambridge, UK}

\affil{$^?$Astronomy Department, UC Berkeley}

\affil{$^?$Naval Research Laboratory}

>>>>

\author{
%
David S. Spiegel\altaffilmark{1, 2} \\
%
{\bf and some order:} \\
%
Jason Nordhaus\altaffilmark{3} \\
%
Nikku Madhusudhan\altaffilmark{4} \\
%
Mehrdad Mirbabayi\altaffilmark{1} \\
%
Aaron Parsons\altaffilmark{5} \\
%
Tony Mroczkowski\altaffilmark{6} \\
%
Neil Zimmerman\altaffilmark{7}
}

@@

\affil{$^2$Research \& Development, Project Florida Labs,
  New York, NY  10001}

\affil{$^2$Department of Mathematics, Rochester Institute of Technology}

\affil{$^3$Astronomy Department, University of Cambridge, UK}

\affil{$^4$Astronomy Department, UC Berkeley}

\affil{$^5$Naval Research Laboratory}

\affil{$^6$Department of Mechanical and Aerospace Engineering, Princeton University, Princeton, NJ 08544}
